# Process GHG data from gas chromatography

This script calculates gas (carbon dioxide, methane, nitrous oxide) flux
in mg m<sup>-2</sup> s<sup>-1</sup> from gas chromatography data (concentration in ppm) using *dplyr* and *GLDEX* packages, see citation at the end of script.


**1.1 Load libraries.**
```{r}
library("dplyr")
library("GLDEX")
library("prettydoc")
```

**1.2 Set directory and load data.**
```{r}
Path <- setwd("D:/Git/project-3/raw-data/field/")
data <- read.csv("gasvials.csv", header = TRUE)
```

```{r}
knitr::kable(head(data))
```

```{r}
str(data)
```

**1.3 Check and remove missing data by row.**
```{r}
colSums(is.na(data))
data <- na.exclude(data)
```

**1.4 Pick specific bottles (closure time).**  
*This code selects measurements from bottle 113 to bottle 118.*
```{r}
sub <- data %>% filter(Bottle >= 113 & Bottle <= 118)
```

**1.5 Model and calculate standard deviation.**
```{r}
m1 <- lm(CH4 ~ dt, data = sub)
coef(m1)
sd2 <- sd(m1$fitted.values)
```

**1.6 Plot regression line and observations.**
```{r}
plot(CH4 ~ dt, data = sub)
abline(m1, col = "blue", lwd = 2)
abline(m1$coefficients[1] + sd2, m1$coefficients[2])
abline(m1$coefficients[1] - sd2, m1$coefficients[2])
```

**1.7. Remove observations as necessary and refit model with sub1. If removal is not necessary, use the rest of script with sub instead of sub1.**  
*This code removes rows 1 and 4 from the sub dataset.*
```{r}
sub1 <- sub[-c(1,4),]
m1 <- lm(CH4 ~ dt, data = sub1)
coef(m1)
sd2 <- sd(m1$fitted.values)
plot(CH4 ~ dt, data = sub1)
abline(m1, col = "blue", lwd = 2)
abline(m1$coefficients[1] + sd2, m1$coefficients[2])
abline(m1$coefficients[1] - sd2, m1$coefficients[2])
```

**1.8 Add fitted values to dataframe.**
```{r}
sub1$CH4fitted <- fitted(m1)
```

**1.9 Calculate and add fitted diff to dataframe.**
```{r}
sub1$CH4diff <- sub1$CH4fitted - 
  lag(sub1$CH4fitted, default = first(sub1$CH4fitted))
```

**1.10 Flux calculation.**  
*This code calculates CH<sub>4</sub> flux in mg CH<sub>4</sub> m<sup>-2</sup> s<sup>-1</sup>.*  
*Remember to adjust the flux calculation according to the gas respective molar mass, CO<sub>2</sub> = 44.01, N<sub>2</sub>O = 44.013, CH<sub>4</sub> = 16.042.*
```{r}
flux <- sub1$CH4diff * 16.042 * sub1$Pressure * 
  273.15 / (22.414 * 1013 *(sub1$ST + 273.15)) *
  (sub1$ChamberV / sub1$CollarA) / sub1$dts
```

**1.11 Remove NaN and false zeros.**
```{r}
df <- as.data.frame(flux)
df <- na.omit(df)
df <- fun.zero.omit(df)
```

**1.12 Write down average flux for chosen bottles.**  
*The mean flux for bottles 113-118 is*
```{r}
mean(df$flux)
```

