# Process chamber-based soil GHG flux data from gas chromatography and from Vaisala 
## GHG data from gas chromatography

This script calculates gas (carbon dioxide, methane, nitrous oxide) flux
in mg m<sup>-2</sup> s<sup>-1</sup> from gas chromatography data (concentration in ppm) using a linear regression fit.


```{r message = FALSE}
#Load libraries
library("readbulk")
library("plyr")
library("dplyr")
library("minpack.lm")
library("GLDEX")

#Set directory and load data
Path <- setwd("D:/Git/project-3/raw-data/field/")
data <- read.csv("gasvials.csv", header = TRUE)
head(data)
str(data)

#Check and remove missing data by row
colSums(is.na(data))
data <- na.exclude(data)

#Pick specific bottles (closure time) 
#This code selects measurements from bottle 113 to bottle 118
sub <- data %>% filter(Bottle >= 113 & Bottle <= 118)

#Model and calculate standard deviation
m1 <- lm(CH4 ~ dt, data = sub)
coef(m1)
sd2 <- sd(m1$fitted.values)

#Plot regression line and observations
plot(CH4 ~ dt, data = sub)
abline(m1, col = "blue", lwd = 2)
abline(m1$coefficients[1] + sd2, m1$coefficients[2])
abline(m1$coefficients[1] - sd2, m1$coefficients[2])

##Remove observations as necessary and refit model with sub1.
#If removal is not necessary, use the rest of script with sub instead of sub1 
#This code removes rows 1 and 4 from the sub dataset
sub1 <- sub[-c(1,4),]
m1 <- lm(CH4 ~ dt, data = sub1)
coef(m1)
sd2 <- sd(m1$fitted.values)
plot(CH4 ~ dt, data = sub1)
abline(m1, col = "blue", lwd = 2)
abline(m1$coefficients[1] + sd2, m1$coefficients[2])
abline(m1$coefficients[1] - sd2, m1$coefficients[2])

#Add fitted values to dataframe
sub1$CH4fitted <- fitted(m1)

#Calculate and add fitted diff to dataframe
sub1$CH4diff <- sub1$CH4fitted - 
  lag(sub1$CH4fitted, default = first(sub1$CH4fitted))
```

**Flux calculation**  
*This code calculates CH<sub>4</sub> flux in mg CH<sub>4</sub> m<sup>-2</sup> s<sup>-1</sup>*  
*Remember to adjust the flux calculation according to the gas respective molar mass, CO<sub>2</sub> = 44.01, N<sub>2</sub>O = 44.013, CH<sub>4</sub> = 16.042*
```{r message = FALSE}
flux <- sub1$CH4diff * 16.042 * sub1$Pressure * 
  273.15 / (22.414 * 1013 *(sub1$ST + 273.15)) *
  (sub1$ChamberV / sub1$CollarA) / sub1$dts

#Remove NaN and false zeros
df <- as.data.frame(flux)
df <- na.omit(df)
df <- fun.zero.omit(df)
```

**Write down average flux for chosen bottles**  
*The mean flux for bottles 113-118 is*
```{r message = FALSE}
mean(df$flux)
```

