# Process CO<sub>2</sub> data from the Vaisala instrument

This script calculates carbon dioxide flux in mg m<sup>-2</sup> s<sup>-1</sup> from the Vaisala instrument (concentration in ppm) using a linear regression fit.

**2.1 Set directory and load data.**
```{r}
raw_data <- read_bulk(directory = "D:/Git/project-3/raw-data/vaisala-raw/",
                      subdirectories = c("01", "02", "03", "04"),
                      extension = ".csv")
```

**2.2 Replace values in "column T.II....C" with the non-NA values from column "TGAS.I....C" creating new column "TempChamber".**
```{r}
raw_data$TempChamber <- ifelse(is.na(raw_data$T.II....C),
                               raw_data$TGAS.I....C, raw_data$T.II....C)
```

**2.3 Rename variables to nicer things.**
```{r}
names(raw_data)[names(raw_data) == "X"] <- "Time"
names(raw_data)[names(raw_data) == "CO2.I...ppm"] <- "CO2"
names(raw_data)[names(raw_data) == "RH.II...."] <- "RH"
names(raw_data)[names(raw_data) == "Subdirectory"] <- "Vaisala"
```

**2.4 Removing unnecessary columns.**  
*This code removes 3rd and 7th columns.*
```{r}
raw_data <- select(raw_data, -c(3, 7))
```

**2.5 Grab metadata (same path as Path above).**
```{r}
fl <- dir("D:/Git/project-3/raw-data/vaisala-raw/")[grepl('\\.csv$', dir("D:/Git/project-3/raw-data/vaisala-raw/"))]
fl <- paste("D:/Git/project-3/raw-data/vaisala-raw/", fl, sep = '')
meta <- do.call(rbind,
                lapply(fl, read.csv, as.is = TRUE))
```

**2.6 Merge datasets by file name keeping order.**
```{r}
names(meta)[names(meta) == "ï..File"] <- "File"
proc_data <- join(raw_data, meta,
                type = "inner")
```

**2.7 Remove missing Vaisala data.**
```{r}
colSums(is.na(proc_data))
proc_data <- na.exclude(proc_data)
```

**2.8 Calibrate CO2 according to Vaisala**
```{r}
proc_data$CO2calib <- with (proc_data, (CO2 - Calib1) / Calib2)
```

**2.9 To calculate dt we need to to convert Time from factor to POSIXct.**
```{r}
proc_data$Datetime <- as.POSIXct(paste(proc_data$Time,tz = ""),
                                 format = "%d/%m/%Y %H:%M:%S")
```

**2.10 Pick specific Vaisala and closure (file).**  
*This code picked Vaisala 4 and closure 8.*
```{r}
sub <- subset(proc_data, Vaisala == "04" & Closure == "8")
sub$dt <- as.numeric(sub$Datetime - sub$Datetime[1])
model1 <- lm(CO2calib ~ dt, data = sub)
plot(CO2calib ~ dt, data = sub)
abline(model1, col = "blue", lwd = 2)
```

**2.11 Add fitted values to dataframe.**
```{r}
sub$CO2fitted <- fitted(model1)
```

**2.12 Calculate average CO2.**
```{r}
flux <- as.numeric(coef(model1)[2] *
                     (sub$ChamberV / sub$CollarA) *
                     (44.01 / 22.414) * (273.15 / (273.15 + sub$Temp)))
```
*The mean flux for Vaisala 4 and enclosure 8 is*
```{r}
mean(flux)
```






